Analytic Occultation Light Curves in Reflected Light

### 2020-04-13 tex/ms.tex
added integral t

\subsection{The integral along the occultor limb, $\pT$}
\label{sec:pT}
%
In this section we present a solution to Equation~(\ref{eq:pT}). The first
order of business is to derive expressions for the integration limits
$\pmb{\phi}$. Depending on the integration case, these limits will correspond
to the point of intersection between the limb of the occultor and the
limb of the occulted body and/or the point of intersection between the limb
of the occultor and the terminator of the occulted body.
The former is given by
\citep[c.f. Equation~24 in][]{Luger2019}
%
\begin{align}
    \phi_l & = \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
    \quad,
\end{align}
%
where the sign is chosen such that the point
$(r_o\cos\phi_l, b_o + r_o\sin\phi_l)$ is on the dayside of the occulted body,
and the latter (of which there may be multiple) is given by
%
% Introduce the function
% %
% \begin{proof}{}
%     \textrm{\faAdjust}(x, y) &=
%     \begin{cases}
%         \textrm{\faCircleO} & \qquad -x \sin\theta' + y\cos\theta' \ge b \sqrt{1 - (x\cos\theta' + y\sin\theta') ^ 2}
%         \\
%         \textrm{\faCircle}  & \qquad \text{otherwise}
%     \end{cases}
% \end{proof}
% %
% which returns \faCircleO\ if point $(x, y)$ is on the dayside of the body and
% \faCircle\ if it is on the nightside.
%
%
\begin{align}
    \pmb{\phi_t} & =
    \theta' +
    \atantwo
    \left(b\sqrt{1 - {\mathbf{x''}}^2 - y''_o}, \mathbf{x''} - x''_o\right)
    \quad
\end{align}
%
where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
These angles are then sorted and placed in the vector $\pmb{\phi}$ such that
the integration is always performed in a counter-clockwise sense about
the center of the integration region.
%
The left panel in Figure~\ref{fig:geometry} shows a configuration in which
the lower integration limit $\phi_0 = 158.2^\circ$ corresponds to the
point of intersection between the limbs of the two bodies and the upper
integration limit $\phi_1 = 223.3^\circ$ corresponds to the
limb-terminator intersection. Both angles are measured counter-clockwise
from the $x'$-axis.

@@

In order to solve Equation~(\ref{eq:J}), it is possible to
replace the complete elliptic integrals $K(k^2)$ and $E(k^2)$ in the lower
boundary conditions \citep[Equation D46 in ][]{Luger2019} with the
incomplete elliptic integrals $\mathbf{F}(k^2, \vkappa)$ and
$\mathbf{E}(k^2, \vkappa)$,
then use the same upward
recursion relation to obtain analytic solutions for all $\iJ_v$:
%
\begin{proof}{J}
    \label{eq:Jrec}
    \iJ_0(k^2, \vkappa) &=
    \frac{1}{3} \bigg(
    2 \left(2 - \frac{1}{k^2}\right) \DE +
    \left(\frac{1}{k^2} - 1\right) \DF +
    \Delta \mathbf{z}_0(k^2, \vkappa)
    \bigg)
    %
    \nonumber \\
    %
    \iJ_1(k^2, \vkappa) &=
    \frac{1}{15} \bigg(
    \left(-3 k^2 + 13 - \frac{8}{k^2}\right) \DE +
    \nonumber \\
    &\qquad\quad\quad\quad\quad\quad\quad\quad\quad
    \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
    \Delta \mathbf{z}_1(k^2, \vkappa)
    \bigg)
    %
    \nonumber \\
    %
    \iJ_v(k^2, \vkappa) &=
    \frac{1}{2v + 3}
    \bigg(
    2 \left( v + 1 + (v - 1) k^2 \right) \iJ_{v - 1} -
    (2v - 3) k^2 \iJ_{v - 2}
    + \Delta \mathbf{z}_v(k^2, \vkappa)
    \bigg)
\end{proof}
%
%
where the last expression is valid for all $v > 1$ and
%
\begin{proof}{J}
    \label{eq:Jrec_z}
    \mathbf{z}_0(k^2, \pmb{\kappa}) & =
    \frac{
        \sinhalfkap
        \coshalfkap
        \mathbf{q}(k^2, \vkappa)
    }{
        k^2
    }
    %
    \nonumber\\
    %
    \mathbf{z}_1(k^2, \pmb{\kappa}) & =
    \left(\left(3 \sinhalfkap[2] + 4\right) - 6k^2\right)
    \mathbf{z}_0(k^2, \pmb{\kappa})
    %
    \nonumber\\
    %
    \mathbf{z}_v(k^2, \pmb{\kappa}) & =
    k^2
    \sinhalfkap[2v - 3]
    \coshalfkap
    \mathbf{q}(k^2, \pmb{\kappa})^5
    \quad,
\end{proof}
%
with
%
\begin{align}
    \label{eq:q}
    \mathbf{q}(k^2, \vkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
    \quad.
\end{align}
%
However, in practice we find that this procedure is even more numerically
unstable than it was in \citet{Luger2019}.
To address this, we express the recurrence structure of the problem as
a tridiagonal system with one lower boundary condition $\iJ_0$
and one upper boundary condition $\iJ_\vmax$:
%
\begin{proof}{J}
    \label{eq:Jtri}
    \begin{pmatrix}
        a_0 & 1   &     &        &         &         \\
        b_1 & a_1 & 1   &        &         &         \\
            & b_2 & a_2 & 1      &         &         \\
            &     & b_0 & a_3    & 1       &         \\
            &     &     & \ddots & \ddots  & \ddots  \\
            &     &     &        & b_\vmax & a_\vmax
    \end{pmatrix}
    \begin{pmatrix}
        \iJ_1           \\
        \iJ_2           \\
        \iJ_3           \\
        \iJ_4           \\
        \cdot\cdot\cdot \\
        \iJ_{\vmax-1}
    \end{pmatrix}
    =
    \begin{pmatrix}
        c_0 - b_0 \iJ_0 \\
        c_1             \\
        c_2             \\
        c_3             \\
        \cdot\cdot\cdot \\
        c_\vmax - \iJ_\vmax
    \end{pmatrix}
\end{proof}
%
where the recursion coefficients are given by
%
\begin{proof}{J}
    \label{eq:Jtri_coeffs}
    a_v(k) &= -2\frac{(v + 1) + (v - 1) k^2}{2v + 3} \nonumber \\
    b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
    c_v(k^2, \vkappa) &= \Delta
    \bigg(
    \frac{
            \mathbf{z}_v(k^2, \pmb{\kappa})
        }{
            2v + 3
        }
    \bigg)
    \quad.
\end{proof}
%
Solving this matrix system yields values for all
intermediate $\{ \iJ_1, {\cdot\cdot\cdot}, \iJ_{\vmax - 1} \}$.
While efficient algorithms exist for solving tridiagonal problems, we obtain
far better numerical stability by instead performing traditional LU
decomposition. We find that this algorithm is stable in all the regimes that we
tested.

@@

\subsubsection{The vector $\viW$}
\label{sec:W}
%
The components of the vector $\viW$ are given by the integral
%
\begin{align}
    \label{eq:W}
    \iW_v(k^2, \vkappa) =
    \vint{\vkappa}{
        \cos\varphi\sin^{2v + 1}\varphi
        \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    }
    \quad.
\end{align}
%
We may compute it by either upward or downward recursion. In both cases,
we compute each of the $\iW_v$ from
%
\begin{proof}{W}
    \iW_v(k^2, \vkappa) = \Delta \mathbf{b}_v(k^2, \vkappa)
    \quad.
\end{proof}
%
In the upward case, we start with the lower boundary conditions
%
\begin{proof}{W}
    \mathbf{b}_0(k^2, \vkappa) &=
    \frac{\sinhalfkap[2]}{5}
    \left(
    \frac{1 - \mathbf{q}(k^2, \vkappa)^3}{1 - \mathbf{q}(k^2, \vkappa)^2}
    +
    \mathbf{q}(k^2, \vkappa)^3
    \right)
    \nonumber \\
    \mathbf{c}_0(k^2, \vkappa) & =
    \sinhalfkap[4]
    \frac{\mathbf{q}(k^2, \vkappa)^5}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \quad,
\end{proof}
%
and recurse upward in $\mathbf{b}$ and $\mathbf{c}$ simultaneously:
%
\begin{proof}{W}
    \mathbf{b}_v(k^2, \vkappa) & =
    \frac{1}{2v + 5}
    \left(
    \frac{2 v \sinhalfkap[2]}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \mathbf{b}_{v - 1}(k^2, \vkappa)
    - \mathbf{c}_{v - 1}(k^2, \vkappa)
    \right)
    \nonumber
    \\
    \mathbf{c}_v(k^2, \vkappa) & =
    \sinhalfkap[2] \mathbf{c}_{v - 1}(k^2, \vkappa)
\end{proof}
%
for $v > 0$.
%
In the case of downward recursion, we start with the upper boundary
conditions
%
\begin{proof}{W}
    \mathbf{b}_\vmax &=
    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{4\vmax + 10}
    \left(
    \mathbf{f}_\vmax(k^2, \vkappa)
    + 2 \mathbf{q}(k^2, \vkappa)^3
    \right)
    \nonumber \\
    \mathbf{c}_\vmax &=
    \frac{1}{2}
    \mathbf{q}(k^2, \vkappa)^5
    \sin^{2\vmax}\left(\frac{\vkappa}{2}\right)
    \quad,
\end{proof}
%
where
%
\begin{proof}{W}
    \mathbf{f}_v(k^2, \vkappa)
    &\equiv
    \frac{3}{v+1}
    \,
    {_2\mathbf{F}_1}\left(
    -\frac{1}{2},
    v + 1;
    v + 2;
    1 - \mathbf{q}(k^2, \vkappa)^2
    \right)
\end{proof}
%
and ${_2\mathbf{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
hypergeometric function.
%
We recurse downward in $\mathbf{b}$ and $\mathbf{c}$ simultaneously:
%
\begin{proof}{W}
    \mathbf{b}_v(k^2, \vkappa) & =
    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{\sinhalfkap[2]}
    \left(1 + \frac{5}{2v + 2}\right)
    \mathbf{b}_{v + 1}(k^2, \vkappa) +
    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{v + 1}
    \nonumber
    \\
    \mathbf{c}_v(k^2, \vkappa) & =
    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{\sinhalfkap[2]}
    \quad.
\end{proof}

>>>>

\subsection{The integral along the occultor limb, $\pT$}
\label{sec:pT}
%
In this section we present a solution to Equation~(\ref{eq:pT}). The first
order of business is to derive expressions for the integration limits
$\pmb{\phi}$. Depending on the integration case, these limits will correspond
to the point of intersection between the limb of the occultor and the
limb of the occulted body and/or the point of intersection between the limb
of the occultor and the terminator of the occulted body.
The former is given by
\citep[c.f. Equation~24 in][]{Luger2019}
%
\begin{align}
    \phi_0 & = \frac{\pi}{2} \pm \left(\arcsin\left(\frac{1 - r_o ^ 2 - b_o ^ 2}{2 b_o r_o}\right) - \frac{\pi}{2}\right)
    \quad,
\end{align}
%
where the sign is chosen such that the point
$(r_o\cos\phi_l, b_o + r_o\sin\phi_l)$ is on the dayside of the occulted body,
and the latter (of which there may be multiple) is given by
%
% Introduce the function
% %
% \begin{proof}{}
%     \textrm{\faAdjust}(x, y) &=
%     \begin{cases}
%         \textrm{\faCircleO} & \qquad -x \sin\theta' + y\cos\theta' \ge b \sqrt{1 - (x\cos\theta' + y\sin\theta') ^ 2}
%         \\
%         \textrm{\faCircle}  & \qquad \text{otherwise}
%     \end{cases}
% \end{proof}
% %
% which returns \faCircleO\ if point $(x, y)$ is on the dayside of the body and
% \faCircle\ if it is on the nightside.
%
%
\begin{align}
    \pmb{\phi_1} & =
    \theta' +
    \atantwo
    \left(b\sqrt{1 - {\mathbf{x''}}^2 - y''_o}, \mathbf{x''} - x''_o\right)
    \quad
\end{align}
%
where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
These angles are then sorted and placed in the vector $\pmb{\phi}$ such that
the integration is always performed in a counter-clockwise sense about
the center of the integration region.
%
The left panel in Figure~\ref{fig:geometry} shows a configuration in which
the lower integration limit $\phi_0 = 158.2^\circ$ corresponds to the
point of intersection between the limbs of the two bodies and the upper
integration limit $\phi_1 = 223.3^\circ$ corresponds to the
limb-terminator intersection. Both angles are measured counter-clockwise
from the $x'$-axis.

@@

In order to solve Equation~(\ref{eq:J}), it is possible to
replace the complete elliptic integrals $K(k^2)$ and $E(k^2)$ in the lower
boundary conditions \citep[Equation D46 in ][]{Luger2019} with the
incomplete elliptic integrals $\mathbbb{F}(k^2, \vkappa)$ and
$\mathbbb{E}(k^2, \vkappa)$,
then use the same upward
recursion relation to obtain analytic solutions for all $\iJ_v$:
%
\begin{proof}{J}
    \label{eq:Jrec}
    \iJ_0(k^2, \vkappa) &=
    \frac{1}{3} \bigg(
    2 \left(2 - \frac{1}{k^2}\right) \DE +
    \left(\frac{1}{k^2} - 1\right) \DF +
    \Delta \mathbf{z}_0(k^2, \vkappa)
    \bigg)
    %
    \nonumber \\
    %
    \iJ_1(k^2, \vkappa) &=
    \frac{1}{15} \bigg(
    \left(-3 k^2 + 13 - \frac{8}{k^2}\right) \DE +
    \nonumber \\
    &\qquad\quad\quad\quad\quad\quad\quad\quad\quad
    \left(3 k^2 - 7 + \frac{4}{k^2}\right) \DF +
    \Delta \mathbf{z}_1(k^2, \vkappa)
    \bigg)
    %
    \nonumber \\
    %
    \iJ_v(k^2, \vkappa) &=
    \frac{1}{2v + 3}
    \bigg(
    2 \left( v + 1 + (v - 1) k^2 \right) \iJ_{v - 1} -
    (2v - 3) k^2 \iJ_{v - 2}
    + \Delta \mathbf{z}_v(k^2, \vkappa)
    \bigg)
\end{proof}
%
%
where the last expression is valid for all $v > 1$ and
%
\begin{proof}{J}
    \label{eq:Jrec_z}
    \mathbf{z}_0(k^2, \pmb{\kappa}) & =
    \frac{
        \sinhalfkap
        \coshalfkap
        \mathbf{q}(k^2, \vkappa)
    }{
        k^2
    }
    %
    \nonumber\\
    %
    \mathbf{z}_1(k^2, \pmb{\kappa}) & =
    \left(\left(3 \sinhalfkap[2] + 4\right) - 6k^2\right)
    \mathbf{z}_0(k^2, \pmb{\kappa})
    %
    \nonumber\\
    %
    \mathbf{z}_v(k^2, \pmb{\kappa}) & =
    k^2
    \sinhalfkap[2v - 3]
    \coshalfkap
    \mathbf{q}(k^2, \pmb{\kappa})^5
    \quad,
\end{proof}
%
with
%
\begin{align}
    \label{eq:q}
    \mathbf{q}(k^2, \vkappa) = \sqrt{1 - \frac{\sinhalfkap[2]}{k^2}}
    \quad.
\end{align}
%
However, in practice we find that this procedure is even more numerically
unstable than it was in \citet{Luger2019}.
To address this, we express the recurrence structure of the problem as
a tridiagonal system with one lower boundary condition $\iJ_0$
and one upper boundary condition $\iJ_\vmax$:
%
\begin{proof}{J}
    \label{eq:Jtri}
    \begin{pmatrix}
        a_0 & 1   &     &        &         &         \\
        b_1 & a_1 & 1   &        &         &         \\
            & b_2 & a_2 & 1      &         &         \\
            &     & b_0 & a_3    & 1       &         \\
            &     &     & \ddots & \ddots  & \ddots  \\
            &     &     &        & b_\vmax & a_\vmax
    \end{pmatrix}
    \begin{pmatrix}
        \iJ_1           \\
        \iJ_2           \\
        \iJ_3           \\
        \iJ_4           \\
        \cdot\cdot\cdot \\
        \iJ_{\vmax-1}
    \end{pmatrix}
    =
    \begin{pmatrix}
        c_0 - b_0 \iJ_0 \\
        c_1             \\
        c_2             \\
        c_3             \\
        \cdot\cdot\cdot \\
        c_\vmax - \iJ_\vmax
    \end{pmatrix}
\end{proof}
%
where the recursion coefficients are given by
%
\begin{proof}{J}
    \label{eq:Jtri_coeffs}
    a_v(k) &= -2\frac{(v + 1) + (v - 1) k^2}{2v + 3} \nonumber \\
    b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
    c_v(k^2, \vkappa) &= \Delta
    \bigg(
    \frac{
            \mathbf{z}_v(k^2, \pmb{\kappa})
        }{
            2v + 3
        }
    \bigg)
    \quad.
\end{proof}
%
Solving this matrix system yields values for all
intermediate $\{ \iJ_1, {\cdot\cdot\cdot}, \iJ_{\vmax - 1} \}$.
While efficient algorithms exist for solving tridiagonal problems, we obtain
far better numerical stability by instead performing traditional LU
decomposition. We find that this algorithm is stable in all the regimes that we
tested.

@@

\subsubsection{The vector $\viW$}
\label{sec:W}
%
The components of the vector $\viW$ are given by the integral
%
\begin{align}
    \label{eq:W}
    \iW_v(k^2, \vkappa) =
    \vint{\vkappa}{
        \cos\varphi\sin^{2v + 1}\varphi
        \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    }
    \quad.
\end{align}
%
We may compute it by either upward or downward recursion. In both cases,
we compute each of the $\iW_v$ from
%
\begin{proof}{W}
    \iW_v(k^2, \vkappa) = \Delta \mathbf{b}_v(k^2, \vkappa)
    \quad.
\end{proof}
%
In the upward case, we start with the lower boundary conditions
%
\begin{proof}{W}
    \mathbf{b}_0(k^2, \vkappa) &=
    \frac{\sinhalfkap[2]}{5}
    \left(
    \frac{1 - \mathbf{q}(k^2, \vkappa)^3}{1 - \mathbf{q}(k^2, \vkappa)^2}
    +
    \mathbf{q}(k^2, \vkappa)^3
    \right)
    \nonumber \\
    \mathbf{c}_0(k^2, \vkappa) & =
    \sinhalfkap[4]
    \frac{\mathbf{q}(k^2, \vkappa)^5}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \quad,
\end{proof}
%
and recurse upward in $\mathbf{b}$ and $\mathbf{c}$ simultaneously:
%
\begin{proof}{W}
    \mathbf{b}_v(k^2, \vkappa) & =
    \frac{1}{2v + 5}
    \left(
    \frac{2 v \sinhalfkap[2]}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \mathbf{b}_{v - 1}(k^2, \vkappa)
    - \mathbf{c}_{v - 1}(k^2, \vkappa)
    \right)
    \nonumber
    \\
    \mathbf{c}_v(k^2, \vkappa) & =
    \sinhalfkap[2] \mathbf{c}_{v - 1}(k^2, \vkappa)
\end{proof}
%
for $v > 0$.
%
In the case of downward recursion, we start with the upper boundary
conditions
%
\begin{proof}{W}
    \mathbf{b}_\vmax &=
    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{4\vmax + 10}
    \left(
    \mathbf{f}_\vmax(k^2, \vkappa)
    + 2 \mathbf{q}(k^2, \vkappa)^3
    \right)
    \nonumber \\
    \mathbf{c}_\vmax &=
    \frac{1}{2}
    \mathbf{q}(k^2, \vkappa)^5
    \sin^{2\vmax}\left(\frac{\vkappa}{2}\right)
    \quad,
\end{proof}
%
where
%
\begin{proof}{W}
    \mathbf{f}_v(k^2, \vkappa)
    &\equiv
    \frac{3}{v+1}
    \,
    {_2\mathbbb{F}_1}\left(
    -\frac{1}{2},
    v + 1;
    v + 2;
    1 - \mathbf{q}(k^2, \vkappa)^2
    \right)
\end{proof}
%
and ${_2\mathbbb{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
hypergeometric function.
%
We recurse downward in $\mathbf{b}$ and $\mathbf{c}$ simultaneously:
%
\begin{proof}{W}
    \mathbf{b}_v(k^2, \vkappa) & =
    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{\sinhalfkap[2]}
    \left(1 + \frac{5}{2v + 2}\right)
    \mathbf{b}_{v + 1}(k^2, \vkappa) +
    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{v + 1}
    \nonumber
    \\
    \mathbf{c}_v(k^2, \vkappa) & =
    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{\sinhalfkap[2]}
    \quad.
\end{proof}

\subsection{The integral along the terminator, $\tT$}
%
In this section we present a solution to Equation~(\ref{eq:tT}), the
line integral along the day/night terminator of the occulted body. As
before, the first thing we must do is derive expressions for the integration
limits $\pmb{\xi}$.
%
Depending on the integration case, these limits
will corresponds to the point of intersection between the terminator and
the limb of the occultor and/or the point of intersection between the
terminator and the limb of the occulted body. The former is given by
%
\begin{proof}{}
    \pmb{\xi_0} &= \atantwo\left(\sqrt{1 - {\mathbf{x''}}^2}, \mathbf{x''} \right)
\end{proof}
%
where $\mathbf{x''}$ are the roots of the quartic (Equation~\ref{eq:quartic}).
The latter is given by
%
\begin{proof}{}
    \xi_1 &=
    \begin{cases}
        0   & \qquad \qquad (1 - x_o'')^2 + {y_o''}^2 < r_o^2
        \\
        \pi & \qquad \qquad \text{otherwise}
        \quad.
    \end{cases}
\end{proof}
%
As before, these angles are then sorted and placed in the vector
$\pmb{\xi}$ such that the integration is performed counter-clockwise
about the center of the integration region.
%
The middle panel of Figure~\ref{fig:geometry} shows a case where
$\xi_0 = 96.5^\circ$ corresponds to the point of intersection between the occultor
limb and the terminator and $\xi_1 = 0^\circ$ corresponds to the
point where the terminator extends onto the backside of the body.
%
Note, importantly, that unlike $\pmb{\phi}$, the angle $\pmb{\xi}$ is not
measured between the $x$-axis and a point on the curve of $\mathcal{T}$.
Recall that $\pmb{\xi}$ is an angular parameter of the ellipse, so it is
measured in the same way as the eccentric anomaly in a Keplerian orbit:
it is the
angle between the $x$-axis and the perpendicular
projection of a point on the ellipse onto the unit circle
(see Figure~\ref{fig:geometry}).
    \mathbb{t}_n & =
        b\cos\theta'
        \sum\limits_{j=0}^{\frac{\nu}{2}}
        \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
        {_1}Z^{\mu,\nu}_{j,k}(b, \theta')
        \iH_{j + k + 1, l + 1 - j - k}(\pmb{\xi})
        \quad\quad\quad\quad
        - \, \sin\theta'
        \sum\limits_{j=0}^{\frac{\nu}{2}}
        \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
        {_1}Z^{\mu,\nu}_{j,k}(b, \theta')
        \iH_{j + k, l + 2 - j - k}(\pmb{\xi})
         & \qquad \mu, \nu, \, \text{even}
        \frac{1}{3}
        \Delta
        \Bigg(
        \arctan\left( \frac{|b|\sin\vxi}{\cos\vxi} \right)
        \qquad\quad\quad
        - \, \sgn\left({\sin\vxi}\right)
            \arctan
                    \left(\frac{\sin\vxi}{1 + \cos\vxi}\right)^2 + 2 b^2 - 1
                }{2 |b| b_c}
            + |b| b_c \cos\vxi
        \qquad\quad\quad
        + \, \pmb{\phi}(b, \vxi)
        \Bigg)
         & \qquad \mu = \nu = 1
        -b\sin\theta'
        \sum\limits_{j=0}^{l-2}
        {_3}Z^{\mu,\nu}_{j}(b, \theta')
        \iH_{j + 1, l + 1 - j}(\pmb{\xi})
        \quad\quad\quad\quad
        - \, \cos\theta'
        \sum\limits_{j=0}^{l-2}
        {_3}Z^{\mu,\nu}_{j}(b, \theta')
        \iH_{j, l + 2 - j}(\pmb{\xi})
         & \qquad \nu \, \text{odd}, \mu = 1, l \, \text{even}
        -b\sin\theta'
        \sum\limits_{j=0}^{l-3}
        \sin\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
        \iH_{j + 2, l - j}(\pmb{\xi})
        \qquad\qquad\qquad
        b\cos\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
        \iH_{j + 1, l + 1 - j}(\pmb{\xi})
        \quad\quad\quad\quad
        - \, \cos\theta'
        \sum\limits_{j=0}^{l-3}
        \sin\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
        \iH_{j + 1, l + 1 - j}(\pmb{\xi})
        \qquad\qquad\qquad
        b\cos\theta'{_4}Z^{\mu,\nu}_{j}(b, \theta')
        \iH_{j, l + 2 - j}(\pmb{\xi})
         & \qquad \nu \, \text{odd}, \mu = 1, l \, \text{odd}
        b\cos\theta'
        \sum\limits_{j=0}^{\frac{\nu}{2}}
        \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
        {_2}Z^{\mu,\nu}_{j,k}(b, \theta')
        \iH_{j + k + 1, l + 1 - j - k}(\pmb{\xi})
        \quad\quad\quad\quad
        - \, \sin\theta'
        \sum\limits_{j=0}^{\frac{\nu}{2}}
        \sum\limits_{k=0}^{\frac{\mu + 2}{2}}
        {_2}Z^{\mu,\nu}_{j,k}(b, \theta')
        \iH_{j + k, l + 2 - j - k}(\pmb{\xi})
         & \qquad \text{otherwise}
    {_1}Z^{\mu,\nu}_{j,k}(b, \theta') & =
    \binom{\frac{\nu}{2}}{j}
    \binom{\frac{\mu + 2}{2}}{k}
    (-1)^{\frac{\mu + 2 - 2k}{2}}
    b^{l + 1 - j - k}
    \sin^\frac{\mu + 2 + 2j - 2k}{2}\theta'
    \cos^\frac{\nu - 2j + 2k}{2}\theta'
    {_2}Z^{\mu,\nu}_{j,k}(b, \theta') & =
    \binom{\frac{\nu - 1}{2}}{j}
    \binom{\frac{\mu - 3}{2}}{k}
    (-1)^{\frac{\mu - 3 - 2k}{2}}
    b^{l - 2 - j - k}
    b_c^3
    \sin^\frac{\mu - 3 + 2j - 2k}{2}\theta'
    \cos^\frac{\nu - 1 - 2j + 2k}{2}\theta'
    {_3}Z^{\mu,\nu}_{j}(b, \theta')   & =
    \binom{l - 2}{j}
    (-1)^{l - 2 - j}
    b^{l - 2 - j}
    b_c^3
    \sin^{l - 2 - j}\theta'
    \cos^j\theta'
    {_4}Z^{\mu,\nu}_{j}(b, \theta')   & =
    \binom{l - 3}{j}
    (-1)^{l - 3 - j}
    b^{l - 3 - j}
    b_c^3
    \sin^{l - 3 - j}\theta'
    \cos^j\theta'
    \phi(b, \xi)                      & =
        0               & \qquad 0 \leq \xi < \frac{\pi}{2}     \\
        \pi             & \qquad \frac{\pi}{2} \leq \xi < \pi   \\
        2 |b| b_c       & \qquad \pi < \xi \leq \frac{3\pi}{2}  \\
        \pi + 2 |b| b_c & \qquad \frac{3\pi}{2} \leq \xi < 2\pi
